IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-05 paper/real.tex
capitalize titles.
Spelling
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\section{Real world languages}
\label{sec:real}

@@

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a syscall.
%
Creating a new task with the |sandbox| syscall is corresponds to
\emph{forking} a process.  Here, page tables limit what memory
a task can access: we can ensure there will be no memory (effectively
defining |klone(tS)
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these syscalls are
meaningless.

@@

We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by |targetLangJS|).
%
The direct approach for implementing the embedded language |specLangJS roundrobinf| is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \verb|getElementById|, by attaching them to
the global JS object.
%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

@@

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accomodating these
features lies outside the purview of our formalism.

>>>>

\section{Real World Languages}
\label{sec:real}

@@

In this setting, the combined language of Section~\ref{sec:retrofit}
can be interpreted in the following way: calling from the target
language to the IFC language corresponds to invoking a syscall.
%
Creating a new task with the |sandbox| syscall corresponds to
\emph{forking} a process.  Here, page tables limit what memory
a task can access: we can ensure there will be no memory (effectively
defining |klone(tS)
= tS0|, where |tS0| is the set of pages necessary to bootstrap a
lightweight process.)
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these syscalls are
meaningless.

@@

We describe SWAPI~\cite{swapi}, an implementation of this system for JavaScript
(which we here denote by |targetLangJS|).
%
The direct approach for implementing the embedded language |specLangJS roundrobinf| is
by running multiple instances of the JS runtime, i.e., in
separate OS-level threads.\footnote{
 The Firefox implementation of SWAPI also considers the case where
 tasks share the JavaScript runtime (and are cooperatively scheduled
 on the event-loop), but the heap and execution context of each task
 is disjoint. This is similar to the single-heap language of
 Section~\ref{sec:concrete}.  However, since the heap separation is
 provided by the browser, we do not discuss this further.
 The interested reader is referred to~\cite{swapi} for more details.
}
%
In SWAPI, the IFC language functionality is implemented in the JS
runtime much like browser layout engines implement the DOM, and expose
the new functions, e.g., \verb|getElementById|, by attaching them to
the global JS object.
%
In turn, each task created with |sandbox| is
executed in a separate thread, running a separate, \emph{fresh} instance of our
modified JS runtime.
%
Formally, |sandbox| is defined with |klone(tS) =
tS0|, where |tS0| is the global object corresponding to the standard
JS library (e.g., |tS0| contains \texttt{Object}, \texttt{Array},
etc.).

@@

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accommodating these
features lies outside the purview of our formalism.
